\section*{Talks}
\begin{etaremune}
\item
    \Shaoqing\
    Seeking your interest and going ahead will contribute to success.
    \textit{Xiamen No.1 High School of Fujian}, Xiamen, China.
    May. 19, 2023.
    \invited
\item
    \Shaoqing\
    Do neighborhood boundaries matter for examining the associations between environmental factors and obesity(online).
    \textit{The 29th International Conference on Geoinformatics in 2022, China University of Geosciences(Beijing)}, Beijing, China.
    Aug. 18, 2022.
    \invited
\item
    \Shaoqing\
    The Evaluation of Health Effect of Short-term Exposure to PM2.5 during Spring Festival: A Case Study of 25 Cities in the Yangtze River Delta(online).
    \textit{The Workshop of 16th Spatial Behavior and Planning \& Digitalization and Fine-Grained Governance, Xiamen University}, Xiamen, China.
    Dem. 12, 2020.
    \invited
\item
    \Shaoqing\
    What is geography? From coronavirus disease 2019 to Bei Dou Systems.
    \textit{Lecture for Geography in high school}, Tong An No.1 High School of Fujian, China.
    Aug.. 7, 2020.
\item
    \Shaoqing\
    The Scale Effect, Zoning Effect of Geographical Features, the Modified Areal Unit Problem and the Chanlleges of Spatial Stastistics.
    \textit{11th Chinese R Language Conference, Renmin University of China}, Beijing, China.
    May. 27, 2018.
\item
    \Shaoqing\
    High-Resolution Mapping of Direct CO$_2$ Emissions and Uncertainties at the Urban Scale.
    \textit{The 13th International Symposium on Spatial Accuracy Assessment in Natural Resources and Environmental Sciences(Spatial Accuracy 2018), China National Convention Center}, Beijing, China.
    May. 22, 2018.
\item
    \Shaoqing\
    The Environmental Effect of Urban Form on PM2.5. 
    \textit{The 9th Chinese Landscape Eoclogy workshop, Sanyu Hotel}, Guangzhou, China.
    Nov. 11, 2017.
\item
    \Shaoqing\
    The Assement Platform of Urban Forest Ecosystem Servcie Based on InVEST model and IOT.
    \textit{The 2rd urban environment long-term monitor and sustainable development workshop, Shanghai Normal University}, Shanghai, China.
    Sep. 28, 2017.
    \invited
\item
    \Shaoqing\
    The Criminal Geographical Analysis about Walking Environment of Urban.
    \textit{The Workshop of 12th Spatial Behavior and Planning \& Spatial-Temporal Behavior and Social Planning Research, Beijing Union University}, Beijing, China.
    Nov. 27, 2016.
\item
    \Shaoqing\
    Transportation Planning of Smart City on the Basis of Data Augmentation Design Under the Perspective of Humanism: A Case Study of Fuzhou’S Cangshan District.
    \textit{The 10th annual conference of International Association of China Planning, Peking University}, Beijing, China.
    July. 2, 2016.
\end{etaremune}
